### 2023-03-31 resilience-safe-down.tex
details

%%%%%%%%
\subsection{Case: $\Bad=\uparrow \Bad$.}
%
%		cas exclusion mutuelle
%
\subsubsection{Subcase: $\Safe=\downarrow \Safe$}

example: mutual exclusion.

\begin{theorem}\label{up-down}
The resilience problem is decidable for ideal-effective WSTS with 
$\Safe=\downarrow \Safe$
and $\Bad=\uparrow \Bad$
and
the additional hypothesis that
for all $D \subseteq S$ downward-closed, $\pred^*(D)$ is downward-closed.
% \alain{est-ce que  $\pred(D)$ is downward closed avec D downward closed serait suffisant ? si l'ordre est omega2 alors closbas+inclusion est wqo donc il faudrait juste que la suite croissante $pred^n(D)+le reste$ converge...}
\end{theorem}

>>>>

%%%%%%%%
\subsection{Case: $\Bad=\uparrow \Bad$.}
%
%		cas unbounded counters
%

let us choose $\Bad$ as the set of states from which the counter $c_{mutex}$ is not bounded by $k$.
%			at least one counter is unbounded. 
This set is upward-closed by upward compatibility in VASS.

\subsubsection{Subcase: $\Safe=\downarrow \Safe$}

As an example, let us choose $\Safe=S-\Bad$ then $\Safe=\downarrow \Safe$.

\begin{theorem}\label{up-down}
The resilience problem is decidable for ideal-effective WSTS with 
$\Safe=\downarrow \Safe$
and $\Bad=\uparrow \Bad$
and
the additional hypothesis that
for all downward-closed set $D \subseteq S$, the set $\pred^*(D)$ is downward-closed.
% \alain{est-ce que  $\pred(D)$ is downward closed avec D downward closed serait suffisant ? si l'ordre est omega2 alors closbas+inclusion est wqo donc il faudrait juste que la suite croissante $pred^n(D)+le reste$ converge...}
\end{theorem}
